&nbsp;

### 2021-03-30 README.Rmd
last update before submission

## Available sample size planning methods
* Accuracy In Parameter Estimation (AIPE)
* A-priori precision (APP)
* Predetermined sample size with Bayes factor
* Power curve
* Classical power calculation
* Interval Equivalence Bayes factor
* Region of Practical Equivalence (ROPE)
* Two One‐Sided Tests (TOST)
* Bayes Factor Design Analysis (BFDA)

@@

You can use the R package to determine the sample size with any of the 9 methods that present in the web app. However, it is not possible currently to generate a justification report from the R package. Please see the tutorial paper for example sample size justifications for each method.

@@

The tutorial paper that presents the web application and R package is not reviewed yet.

>>>>

## Available sample size planning methods
* Two One‐Sided Tests (TOST)
* Interval Equivalence Bayes factor
* Classical power analysis
* Power curve
* Bayes Factor Design Analysis (BFDA)
* Predetermined sample size with Bayes factor
* Accuracy In Parameter Estimation (AIPE)
* A-priori precision (APP)
* Region of Practical Equivalence (ROPE)

@@

You can use the R package to determine the sample size with any of the 9 methods that present in the web app. However, it is not possible currently to generate a justification report from the R package. Please see the tutorial paper or the web app for example sample size justifications for each method.

@@

The tutorial paper that presents the web application and R package is not reviewed yet. More details are available in Kovacs, van Ravenzwaaij, Hoekstra & Aczel (2021).

### 2021-03-30 inst/app/www/about.Rmd
last update before submission

The __SampleSizePlanner__ shiny application enables researchers to calculate the sample size with 9 different methods in app and provides code to use an additional method from R. The aim of the app is to make the various sample size calculating methods available for a wide range of researchers and propagate the transparent reporting of the choose method. Therefore, a formatted template text containing the used parameters and the output of the calculations is available for download. This text can be complemented with the reasoning behind each decision.

### Contributors
- Don van Ravenzwaaij
- Marton Kovacs
- Rink Hoekstra
- Balazs Aczel

>>>>

The __SampleSizePlanner__ shiny application enables researchers to calculate the sample size with 9 different methods in app and provides code to use an additional method from R. The aim of the app is to make the various sample size calculating methods available for a wide range of researchers and propagate the transparent reporting of the chosen method. Therefore, a formatted template text containing the used parameters and the output of the calculations is available for download. This text can be complemented with the reasoning behind each decision.

### Contributors
- Marton Kovacs
- Don van Ravenzwaaij
- Rink Hoekstra
- Balazs Aczel
